---
title: "INSERT TITLE HERE"
author: Glen P. Martin^1^, PhD; ....

#bibliography: "../Manuscript/REFs.bib" #path to .bib file for this paper
csl: ../Templates/american-medical-association.csl
#sets the style of the references: more avaliable here: https://github.com/citation-style-language/styles

output: 
  bookdown::word_document2:
    fig_caption: yes
    reference_docx: "../Templates/markdown_manuscript_template.docx"
  
  # bookdown::pdf_document2:
  #   includes:
  #     before_body: "../Templates/doc_prefix.tex"
  #     in_header: "../Templates/preamble.tex"
  #   keep_tex: yes
  #   latex_engine: xelatex
  #   number_sections: yes
  #   toc: no
  
  # github_document:
  #   toc: false

knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_dir = "rmarkdown_output",
  output_format = "all") })
  
fontsize: 12pt
linestretch: 1.5
# link-citations: yes
---

```{r setup, include=FALSE}
library(knitr)

# rstudio sets the folder where .Rmd file is located as work directory
# set it back to the folder where .Rproj is located
opts_knit$set(root.dir = normalizePath("../")) 

opts_chunk$set(echo = FALSE, fig.width = 6, fig.height = 6,
               fig.align = 'center', cache = FALSE, warning = FALSE, 
               message = TRUE)
options(digits = 3, width = 88)
```

```{r env_load, include=FALSE}
#Use this R chunk to call the scripts (this is usually the final script in the "chain" if following the idea of
#splitting each analytical tasks into steps, where each script "calls" the previous)
#e.g. source(here::here("Scripts", "02_Analysis.R"))

```


1. Division of Informatics, Imaging and Data Science, Faculty of Biology, Medicine and Health, University of Manchester, Manchester Academic Health Science Centre, Manchester, United Kingdom

[Insert Additional Affiliations for co-authors]

\
__Running Title:__ [Insert Running Title] 

__Funding:__ [Insert Funding Statement] 

__Competing  Interests:__ [Insert CI Statement] 

__Corresponding Author:__ \
Dr Glen Philip Martin \
Lecturer in Health Data Science \
Vaughan House, University of Manchester, Manchester, M13 9GB, United Kingdom \
Email: glen.martin@manchester.ac.uk

\clearpage

# Abstract


## Keywords


\clearpage


# Background {#Background}


# Methods {#Methods}

# Results {#Results}

# Discussion {#Discussion}



# Tables 

```{r ENTER_TABLE_LABEL}
#e.g. knitr::kable(table1, caption = 'Insert Table Caption')
```


# Figures

```{r ENTER_FIGURE_LABEL, fig.cap="Insert Figure Caption."}
# 
```


# References
